Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-23 ms.tex
greene
beta and efficiency.

\section{Model}
\label{sec:model}
\subsection{Galaxy models}
\label{sec:gal_model}
\citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to
measure the radial surface brightness profiles for hundreds of nearby
early type galaxies. The measured profile is fit by a ``Nuker" law parameterization:
\begin{equation}
  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b},
\end{equation}
i.e., a broken power law that transitions from an inner power law
slope, $\Gamma$, to an outer power law slope, $\beta$, at a break
radius, $\rb$.  If the stellar population is spherically symmetric,
then this corresponds to a 3D stellar density $\rhostar \propto
r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
$r \gg \rb$.  We can write the deprojected stellar density
approximately (formally, this is the $\alpha \rightarrow \infty$
limit) as
\begin{align}
\rho_\star = 
\begin{cases}
\rho_\star|_{\rinf} \left(r/\rinf\right)^{-1-\Gamma} & r \leq r_b\\
\rho_\star|_{r_b} \left(r/r_b\right)^{-1-\beta} & r > r_b,
\label{eq:rhostar}
\end{cases}
\end{align}
where $\rho_\star|_{\rinf}$ is the stellar density at the radius of
the black hole sphere of influence\footnote{This approximate
  expression agrees surprisingly well with the mean empirical scaling
  relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of
  \citet{Stone&Metzger15}, although we note that this relation has
  significant scatter.},
\begin{equation}
  \rinf \simeq G \Mbh/\sigma_{\bullet}^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
\label{eq:rsoi}
\end{equation}
where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the
second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$
relationship of \citet{McConnellMa+:2011a},
 \begin{align}
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma_{\bullet}}{200\,{\rm
      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
\label{eq:Msigma}
\end{align}
Though of questionable validity for low mass black holes (e.g.,
\citealt{Kormendy+2013}), we adopt equation (\ref{eq:Msigma}) for lack
of an obviously better alternative.

@@

We fix $\beta = 2$ because our results are not overly sensitive to the
properties of the gas flow on radial scales $\gtrsim r_b$ {\bf AG:
  beta=1 could be problematic for low heating rates}. The presence of
the break radius $r_{b}$ is, however, necessary to obtain a converged
steady state for some regions of our parameter space.  We consider
solutions calculated for up to four values of $\rb$: 50 pc, 100 pc,
200 pc, and 400 pc, motivated by the range of break radii from the
\citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies the
  break radius follows the scaling relationship $\rb\sim 106 \,
  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
  clear trend with $\Mbh$.}  In practice we calculate solutions for a
range of $\rb$ only in cases when its precise value is expected to
have a significant affect on the solution, in particular for high SMBH
masses and low heating rates, for which the stagnation radius
approaches large radii. We also neglect values of $r_b$ which would
give unphysically large bulges for a given $\Mbh$.

@@

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\eddr\right)^{0.9} & \eddr \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
  0.1 \left(\eddr\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
  0.1 & \eddr \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}

>>>>

\section{Model}
\label{sec:model}
\subsection{Galaxy models}
\label{sec:gal_model}
\citet{LauerFaber+:2007a} use Hubble Space Telescope WFPC2 imaging to
measure the radial surface brightness profiles for hundreds of nearby
early type galaxies. The measured profile is fit by a ``Nuker" law parameterization:
\begin{equation}
  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b},
\end{equation}
i.e., a broken power law that transitions from an inner power law
slope, $\Gamma$, to an outer power law slope, $\beta$, at a break
radius, $\rb$.  If the stellar population is spherically symmetric,
then this corresponds to a 3D stellar density $\rhostar \propto
r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\propto r^{-1-\beta}$ for
$r \gg \rb$.  We can write the deprojected stellar density
approximately (formally, this is the $\alpha \rightarrow \infty$
limit) as
\begin{align}
\rho_\star = 
\begin{cases}
\rho_\star|_{\rinf} \left(r/\rinf\right)^{-1-\Gamma} & r \leq r_b\\
\rho_\star|_{r_b} \left(r/r_b\right)^{-1-\beta} & r > r_b,
\label{eq:rhostar}
\end{cases}
\end{align}
where $\rho_\star|_{\rinf}$ is the stellar density at the radius of
the black hole sphere of influence\footnote{This approximate
  expression agrees surprisingly well with the mean empirical scaling
  relation for $r_{\rm inf}(M_\bullet)$ calculated in Appendix C of
  \citet{Stone&Metzger15}, although we note that this relation has
  significant scatter.},
\begin{equation}
  \rinf \simeq G \Mbh/\sigma_{\bullet}^2 \approx 14 M_{\bullet,8}^{0.6}\,{\rm pc},
\label{eq:rsoi}
\end{equation}
where $M_{\bullet,8} \equiv M_{\bullet}/10^{8}M_{\odot}$ and the
second equality in (\ref{eq:rsoi}) employs the $\Mbh-\sigma$
relationship of \citet{McConnellMa+:2011a},
 \begin{align}
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma_{\bullet}}{200\,{\rm
      km\,s^{-1}}}\right)^{5.1}M_{\odot}.
\label{eq:Msigma}
\end{align}
Though of questionable validity for low mass black holes (e.g.,
\citealt{Greene+2010, Kormendy+2013}), we adopt equation
(\ref{eq:Msigma}) for lack of an obviously better alternative.

@@

We fix $\beta = 2$ but have our results are not overly sensitive to
the properties of the gas flow on radial scales $\gtrsim r_b$ for
$\beta\gsim 1.5$ (this is near the peak of the distribution of $\beta$
in \citet{LauerFaber+:2007a}) {\bf AG: a little more detail}. The
presence of the break radius $r_{b}$ is, however, necessary to obtain
a converged steady state for some regions of our parameter space.  We
consider solutions calculated for up to four values of $\rb$: 50 pc,
100 pc, 200 pc, and 400 pc, motivated by the range of break radii from
the \citet{LauerFaber+:2007a} sample.\footnote{For the core galaxies
  the break radius follows the scaling relationship $\rb\sim 106 \,
  (\Mbheight)^{0.39}$ pc, with scatter of approximately one dex.  Most
  the cusp galaxies have $\rb$ between 100 and 1000 pc, and lack a
  clear trend with $\Mbh$.}  In practice we calculate solutions for a
range of $\rb$ only in cases when its precise value is expected to
have a significant affect on the solution, in particular for high SMBH
masses and low heating rates, for which the stagnation radius
approaches large radii. We also neglect values of $r_b$ which would
give unphysically large bulges for a given $\Mbh$.

@@

\begin{align}
\epsilon_{\rm rad} \simeq 
\begin{cases}
  2.6 \times 10^{-2} \left(\frac{\eddr}{10^{-4}}\right)^{0.9} & \eddr \lsim 10^{-4} \\
  2.6 \times 10^{-2} &  10^{-2} \lsim \eddr \lsim  10^{-4}\\
  0.1 \left(\frac{\eddr}{0.1}\right)^{0.58} &  10^{-2} \lsim \eddr \lsim  0.1\\
  0.1 & \eddr \gsim 0.1
\end{cases}
\label{eq:efficiency}
\end{align}
